Writing a reproducible paper with RStudio and Quarto

### 2023-04-06 paper.qmd
Add results: "asis" to visible code of regression table.

``` {{r}}
#| label: tbl-4
#| tbl-cap: "Linear regression with modelsummary"
library(modelsummary)
M1 <- lm(Fertility ~ Education + Agriculture, data = swiss)
M2 <- lm(Fertility ~ Education + Catholic, data = swiss)
M3 <- lm(Fertility ~ Education + Infant.Mortality + Agriculture, data = swiss)
models <- list("M1" = M1, "M2" =  M2, "M3" = M3)

>>>>

``` {{r}}
#| label: tbl-4
#| tbl-cap: "Linear regression with modelsummary"
#| results: "asis"

library(modelsummary)
M1 <- lm(Fertility ~ Education + Agriculture, data = swiss)
M2 <- lm(Fertility ~ Education + Catholic, data = swiss)
M3 <- lm(Fertility ~ Education + Infant.Mortality + Agriculture, data = swiss)
models <- list("M1" = M1, "M2" =  M2, "M3" = M3)
